{\bfseries Install guide} Change to any folder in your home directory and enter following commands in your terminal.

{\ttfamily git clone {\tt https\+://github.\+com/kit-\/cel/gr-\/radar.\+git}} // clone this repository {\ttfamily cd gr-\/radar/} {\ttfamily mkdir build} // make build folder {\ttfamily cd build/} {\ttfamily cmake ../} // build makefiles {\ttfamily make} // build toolbox

Some testcases use huge buffer sizes. Therefore you have to increse the maximum size of a single shared memory segment. Run following line to fix that. Additionally the script configures some U\+S\+RP stuff. All changes will be resetted after reboot.

{\ttfamily sudo ./../examples/setup/setup\+\_\+core}

Now you can run all testcases and install the toolbox. If {\ttfamily ctest} responds with \textquotesingle{}100\% tests passed\textquotesingle{} the toolbox should be build correctly.

{\ttfamily ctest} // run tests {\ttfamily sudo make install} // install toolbox

{\bfseries Development progress blog} {\tt https\+://grradar.\+wordpress.\+com/}

{\bfseries Documentation} For full documentation build the toolbox and open {\ttfamily build/docs/doxygen/html/index.\+html} in any web browser.

{\bfseries Development platform} G\+NU Radio 3.\+7.\+4 U\+HD 3.\+7.\+2 Ubuntu 14.\+04

{\bfseries Dependencies} Qt 4.\+8.\+6 Qwt 6.\+0.\+0 python-\/matplotlib

Qt and Qwt should be installed with G\+NU Radio. But there can be issues if Qwt is below version 6. python-\/matplotlib is included in some testcases.

{\bfseries Contact} Stefan Wunsch stefan.\+wunsch[at]student.\+kit.\+edu 